Using numerical modelling to investigate temperature and wave exposure as drivers

### 2019-10-16 morphology_paper.Rmd
changed .bib file. one reference.bib will be used from now on. updated latest output of word file

---
title: Using numerical modelling to investigate temperature and wave exposure as drivers
  of macroalgal characteristics
author: "R. Coppin, C. Rautenbach, T. Ponton and A.J Smit"
fontsize: 10pt
output:
  word_document:
    reference_docx: frontiers_template.docx
  pdf_document: 
    fig_caption: yes
geometry: margin=1in
papersize: A4
tables: yes
bibliography: refs_morphology_paper.bib
---

@@

```{r wave variable plot, warning = FALSE, echo=FALSE, message = FALSE, include= TRUE, eval=TRUE,fig.height=7,fig.width=8, fig.cap='\\label{fig:wave variable plot}Mean significant wave height and mean significant peak period across sites and by region. Mean significant wave height across sites is presented in plot A and is represented by solid triangles and standard deviation by the whiskers. Differences in mean significant wave height between regions are presented in plot B. Mean significant peak period across sites is presented in plot C and is represented by solid dots and standard deviation by whiskers. Differences in mena significant peak period between regions are presented in plot D.'}
ggarrange(wave_plot_1,wave_boxplot_1, wave_plot_2, wave_boxplot_2, common.legend = TRUE, labels = c("A", "B", "C", "D"), align = "hv")
```

>>>>

---
title: Using numerical modelling to investigate temperature and wave exposure as drivers
  of macroalgal morphological characteristics
author: "R. Coppin, C. Rautenbach, T. Ponton and A.J Smit"
fontsize: 10pt
output:
  word_document:
    reference_docx: frontiers_template.docx
  pdf_document: 
    fig_caption: yes
geometry: margin=1in
papersize: A4
tables: yes
bibliography: references.bib
---

@@

```{r wave variable plot, warning = FALSE, echo=FALSE, message = FALSE, include= TRUE, eval=TRUE,fig.height=7,fig.width=8, fig.cap='\\label{fig:wave variable plot}Mean significant wave height and mean significant peak period across sites and by region. Mean significant wave height across sites is presented in plot A and is represented by solid triangles and standard deviation by the whiskers. Differences in mean significant wave height between regions are presented in plot B. Mean significant peak period across sites is presented in plot C and is represented by solid dots and standard deviation by whiskers. Differences in mena significant peak period between regions are presented in plot D.'}
ggarrange(wave_plot_1,wave_boxplot_1, wave_plot_2, wave_boxplot_2, common.legend = FALSE, labels = c("A", "B", "C", "D"), align = "hv")
```
